Combinatorial Proofs and Decomposition Theorems for First-order Logic

### 2021-01-15 main.tex
comment
prop encoding

\newcommand{\Gr}{\mathcal{G}}
\newcommand{\PE}[1]{#1^P}

@@

$\vlinf{\faD}{}{\Scons{\forall x.\ttt}}{\Scons\ttt}$

$\vlinf{\axr}{}{\sqn{a,\cneg a}}{}
            \qquad
            \vlinf{\ttt}{}{\sqn{\ttt}}{}
$

@@

%All statements in this section are proved by rule permutation arguments.
\begin{thm}\label{thm:LK1-decompose}
  Let $\Gamma$ be a sequent. If\/ $\sqn\Gamma$ is provable in $\FOLK$ (as depicted on the left below) then there is a sequent
  $\Gamma'$ such that there is a derivation as shown on the right below:\vadjust{\vskip-2ex}
  \begin{equation*}
    \vlderivation{
        \vltrl{}{\FOLK}{\Deri}{\sqns{\Gamma}}{
          \vlhy{\quad}}{
          \vlhy{}}{
          \vlhy{}}}
    \qquad
    \Longrightarrow
    \qquad
    \vlderivation{
      \vlde{\set{\wlD,\wrD,\cD}}{\Deri_2}{\sqns\Gamma}{
        \vltrl{}{\FOMLL}{\Deri_1}{\sqns{\Gamma'}}{
          \vlhy{\quad}}{
          \vlhy{}}{
          \vlhy{}}}}
  \end{equation*}
\end{thm}

@@

\todo{}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Unification Nets}

>>>>

\newcommand{\Gr}{\mathcal{G}}
\newcommand{\PE}[1]{#1^\circ}

@@

@@

%All statements in this section are proved by rule permutation arguments.
\begin{thm}\label{thm:LK1-decompose}
  Let $\Gamma$ be a sequent. If\/ $\sqn\Gamma$ is provable in $\FOLK$ (as depicted on the left below) then there is a sequent
  $\Gamma'$ such that there is a derivation as shown on the right below:\vadjust{\vskip-2ex}
  \begin{equation*}
    \vlderivation{
        \vltrl{}{\FOLK}{\Deri}{\sqns{\Gamma}}{
          \vlhy{\quad}}{
          \vlhy{}}{
          \vlhy{}}}
    \qquad
    \Longrightarrow
    \qquad
    \vlderivation{
      \vlde{\set{\wlD,\wrD,\cD}}{\Deri_2}{\sqns\Gamma}{
        \vltrl{}{\FOMLL}{\Deri_1}{\sqns{\Gamma'}}{
          \vlhy{\quad}}{
          \vlhy{}}{
          \vlhy{}}}}
  \end{equation*}
\end{thm}
\juihsuan{maybe we should take $\form{\Gamma}$ instead? (consider the proof
$\vlderivation{\vlin{\wk}{}{\sqn{\ttt, A}}{
                 \vlin{\ttt}{}{\sqn\ttt}{
                   \vlhy{}}}}$)}

@@

\todo{this has to be moved to the right place at some point}

The \bfit{propositional encoding} $\PE{A}$ of a formula $A$ is defined inductively by:
\begin{equation*}
  \begin{array}{r@{\;=\;}l}
    \PE{a} & a\\
    \PE{(A \cor B)} &  \PE{A} \cor \PE{B} \\
    \PE{(A \cand B)} & \PE{A} \cand \PE{B}
  \end{array}
  \qquad
  \begin{array}{r@{\;=\;}l}
    \PE{(\forall x A)} & u_x \cor \PE{A}\\
    \PE{(\exists x A)} & e_x \cand \PE{A}
  \end{array}
\end{equation*}
where $u_x$ and $e_x$ are fresh nullary atoms. The purpose of the propositional encoding is to simplify some arguments that do not depend on the variable bindings. In particular, observe that $\graphof A$ and $\graphof{\PE A}$ only differ in the labelling of certain vertices.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Unification Nets}
